### 2024-06-06 Scripts/Scripts-collection.Rmd
Update Scripts-collection.Rmd

@@

df_prevalent <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\microbiome_species-top_prevalent.csv)")
df_order <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\microbiome_species-top_prevalent-sorted.csv)")
df_sorted_desc <- arrange(df_order, desc(prevalency_percentage_all))

@@

>>>>

### Figure 1
### --------------------------------------------------------------------------------------------------------------------------------------------

@@

df_prevalent <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\microbiome_species-top_prevalent.csv)")
df_order <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\microbiome_species-top_prevalent-orders.csv)")
df_sorted_desc <- arrange(df_order, desc(prevalency_percentage_all))

@@

tree_phylum_level2 <- read.tree(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\gtdbtk_filtered_satisfied.tree)')
labels_tree_phylogeney.df  <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\ggtree_assembled_bins_metadata_with_hospitals.csv)')
meta_info <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\metadata-assembled_bins.csv)')

### plot the phylogenetic tree and the strip layer(display information about phylum level taxonomy)
p_final_layer1 <- ggtree(tree_phylum_level2, branch.length="none",layout = 'fan',open.angle=18,size=0.3) %<+% labels_tree_phylogeney.df + 
  #Proteobacateria
  geom_strip(taxa1 = "P139-HospitalA_coassembly.001",
             taxa2 = "P122-HospitalA_coassembly.002",
             offset = 8.8,
             barsize = 40,
             extend = 0.5,
             color="#6d9fcd") + #geom_tiplab(size=1.5,align = TRUE,offset = 0.5) + 
  #Acinetobacteria
  geom_strip(taxa1 = "P34-HospitalB_coassembly.037",
             taxa2 = "P38-HospitalB_coassembly.004",
             offset = 8.8,
             barsize = 40,
             extend = 0.5,
             color="#c3e5f5") +
  #Firmicutes
  geom_strip(taxa1 = "P34-HospitalB_coassembly.038",
             taxa2 = "P123-HospitalA_coassembly.005",
             offset = 8.8,
             barsize = 40,
             extend = 0.5,
             color="#A4A7DE") +
  #Firmicutes
  geom_strip(taxa1 = "P34-HospitalB_coassembly.022",
             taxa2 = "P123-HospitalA_coassembly.007",
             offset = 8.8,
             barsize = 40,
             extend = 0.5,
             color="#A4A7DE") +
  #Firmicutes
  geom_strip(taxa1 = "P34-HospitalB_coassembly.027",
             taxa2 = "P34-HospitalB_coassembly.050",
             offset = 8.8,
             barsize = 40,
             extend = 0.5,
             color="#A4A7DE") +
  #Firmicutes
  geom_strip(taxa1 = "P45-HospitalB_coassembly.008",
             taxa2 = "P22-HospitalB_coassembly.002",
             offset = 8.8,
             barsize = 40,
             extend = 0.5,
             color="#A4A7DE") +
  #Bacteroidota
  geom_strip(taxa1 = "P72-HospitalB_coassembly.005",
             taxa2 = "P44-HospitalB_coassembly.009",
             offset = 8.8,
             barsize = 40,
             extend = 0.5,
             color="#ffc3c3") + 
  #Actinobacteriota
  geom_strip(taxa1 = "P34-HospitalB_coassembly.014",
             taxa2 = "P24-HospitalB_coassembly.005",
             offset = 8.8,
             barsize = 40,
             extend = 0.5,
             color="#c3e5f5")

## show collection sites with various star types 
p_final_layer2 <- p_final_layer1 +
  geom_fruit(data=meta_info, geom=geom_star,
             mapping=aes(y=user_genome,x=sampling_site,starshape=sampling_site,fill=sampling_site),
             color = "black", offset=0.30,
             size =2,
             pwidth=0.1,
             grid.params=list(
               linetype=2,
               size=0.5
             )) + scale_fill_manual(values=c("#FFC125","#87CEFA","#7B68EE"),
                                    guide=guide_legend(override.aes = list(size = 8)))  + 
  geom_tiplab(aes(label=species),size=1.7,offset = 1.2) + new_scale_fill()

## show collections sites with various colors
# p_final_layer2 <- p_final_layer1 +
#   geom_fruit(data=meta_info, geom=geom_tile,
#              mapping=aes(y=user_genome,fill=sampling_site),
#              color = "black", offset = 0.5,size = 0.02,width=2.4,) +
#   scale_fill_manual(values=c("#FFC125","#87CEFA","#7B68EE")) + geom_tiplab(size=1.5)
#   
p_final_layer3 <- p_final_layer2 + 
  geom_fruit(data=meta_info, geom=geom_bar,
             mapping=aes(y=user_genome, x=fastani_af, fill=sampling_site),
             offset = 0.05,
             pwidth=0.1,
             width=0.6,
             orientation="y", 
             stat="identity",
             show.legend=F,
             axis.params = list(axis='x',text.size=2,nbreak=2,vjust=1)) +
  scale_fill_manual(values=c("#FFC125","#87CEFA","#7B68EE"))  + new_scale_fill() +
  geom_tippoint(mapping=aes(color=phylum),
                size=1.2,
                show.legend=F) +
  scale_color_manual(values=c("Proteobacteria"="#6d9fcd",
                              "Actinobacteriota"="#c3e5f5",
                              "Firmicutes"="#A4A7DE",
                              "Firmicutes_A"="#A4A7DE",
                              "Firmicutes_C"="#A4A7DE",
                              "Bacteroidota"="#ffc3c3"))

p_final_layer4 <- p_final_layer3 + 
  # Acinetobacter baumannii
  geom_strip(taxa1 = "P123-HospitalA_coassembly.002",
             taxa2 = "P122-HospitalA_coassembly.002",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="#267278",
             alpha=1) +
  # Burkholderia cenocepacia
  geom_strip(taxa1 = "P157-HospitalA_coassembly.003",
             taxa2 = "P66-HospitalB_coassembly.002",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="#65338D",
             alpha=1) +
  geom_strip(taxa1 = "P14-HospitalC_coassembly.002",
             taxa2 = "P6-HospitalC_coassembly.002",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="#65338D",
             alpha=1) +
  # Corynebacterium striatum
  geom_strip(taxa1 = "P121-HospitalA_coassembly.003",
             taxa2 = "P24-HospitalB_coassembly.005",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="#4770B3",
             alpha=1) +
  geom_strip(taxa1 = "P155-HospitalA_coassembly.004",
             taxa2 = "P155-HospitalA_coassembly.004",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="#4770B3",
             alpha=1) +
  # Elizabethkingia anophelis
  geom_strip(taxa1 = "P141-HospitalA_coassembly.002",
             taxa2 = "P141-HospitalA_coassembly.001",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="#D21F75",
             alpha=1) +
  # Enterococcus_B faecium
  geom_strip(taxa1 = "P96-HospitalB_coassembly.002",
             taxa2 = "P76-HospitalB_coassembly.001",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="#3B3689",
             alpha=1) +
  # Klebsiella pneumoniae
  geom_strip(taxa1 = "P116-HospitalA_coassembly.002",
             taxa2 = "P155-HospitalA_coassembly.002",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="#50AED3",
             alpha=1) +
  geom_strip(taxa1 = "P115-HospitalA_coassembly.001",
             taxa2 = "P156-HospitalA_coassembly.002",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="#50AED3",
             alpha=1)+
  geom_strip(taxa1 = "P96-HospitalB_coassembly.001",
             taxa2 = "P96-HospitalB_coassembly.001",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="#50AED3",
             alpha=1) +
  # Porphyromonas pasteri
  geom_strip(taxa1 = "P121-HospitalA_coassembly.002",
             taxa2 = "P32-HospitalB_coassembly.008",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="#48B24F",
             alpha=1) +
  # Prevotella melaninogenica
  geom_strip(taxa1 = "P23-HospitalB_coassembly.006",
             taxa2 = "P45-HospitalB_coassembly.006",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="#E57438",
             alpha=1) +
  geom_strip(taxa1 = "P50-HospitalB_coassembly.004",
             taxa2 = "P34-HospitalB_coassembly.003",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="#E57438",
             alpha=1) +
  # Prevotella oris
  geom_strip(taxa1 = "P72-HospitalB_coassembly.013",
             taxa2 = "P47-HospitalB_coassembly.010",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="#569DD2",
             alpha=1) +
  # Pseudomonas aeruginosa
  geom_strip(taxa1 = "P20-HospitalC_coassembly.001",
             taxa2 = "P152-HospitalA_coassembly.004",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="#569D79",
             alpha=1) +
  # Stenotrophomonas maltophilia
  geom_strip(taxa1 = "P105-HospitalB_coassembly.003",
             taxa2 = "P139-HospitalA_coassembly.001",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="#58595B",
             alpha=1) + 
  # Haemophilus influenzae
  geom_strip(taxa1 = "P54-HospitalB_coassembly.001",
             taxa2 = "P44-HospitalB_coassembly.002",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="black",
             alpha=1) + 
  # Slackia exigua
  geom_strip(taxa1 = "P45-HospitalB_coassembly.020",
             taxa2 = "P72-HospitalB_coassembly.026",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="black",
             alpha=1) + 
  # Staphylococcus aureus
  geom_strip(taxa1 = "P34-HospitalB_coassembly.029",
             taxa2 = "P155-HospitalA_coassembly.010",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="black",
             alpha=1) + 
  # Streptococcus anginosus
  geom_strip(taxa1 = "P80-HospitalB_coassembly.001",
             taxa2 = "P80-HospitalB_coassembly.001",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="black",
             alpha=1) +
  geom_strip(taxa1 = "P112-HospitalA_coassembly.001",
             taxa2 = "P112-HospitalA_coassembly.001",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="black",
             alpha=1) +
  geom_strip(taxa1 = "P47-HospitalB_coassembly.004",
             taxa2 = "P47-HospitalB_coassembly.004",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="black",
             alpha=1) +
  # Streptococcus constellatus
  geom_strip(taxa1 = "P45-HospitalB_coassembly.009",
             taxa2 = "P50-HospitalB_coassembly.005",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="black",
             alpha=1) +
  geom_strip(taxa1 = "P102-HospitalB_coassembly.006",
             taxa2 = "P102-HospitalB_coassembly.006",
             offset = 29,
             barsize =0.8,
             extend = 0.5,
             color="black",
             alpha=1)
